---
title: "Bar Graph 1: Landscape of Arts Education Nonprofits"
author: "Steven Todd McIntyre II"
date: "2026-02-23"
runtime: shiny
format: 
  dashboard:
    embed-resources: true
    theme: minty
    output:
      orientation: columns
execute:
  warning: false
  message: false
  echo: false
---

```{r}
library(tidyverse)
library(tidytext)
library(here)
library(knitr)
library(shiny)
library(rio)
```

# Visualization

## Column

```{r}
a25 <- import(here("data/BMF_A25.csv"))

a25 |>
  unnest_tokens(output = words, input = ORG_NAME_CURRENT) |>
  select(words) |>
  filter(!words %in% stop_words$word) |>
  count(words) |>
  mutate(words = fct_lump_n(words, n=50, w=n)) |>
  filter(words != "Other") |>
  group_by(words) |>
  summarize(n = sum(n)) |>
  mutate(words=fct_reorder(words, n)) |>
  ggplot(aes(n, words)) +
  geom_col() +
  labs(
    title = "Top 50 Words in A25 \"Arts Education\" Organization Names",
    x = "Instances in A25 Organization Names",
    y = ""
  ) +
  theme(
    axis.text.y = element_text(size = 4)
  )

```

# Summary of Updates

## Column

Removing the relatively poor visualization that was mostly intended to test embed-resources, I've now added a visualization that will be, in some form, in my final project.

Welcome!

Today, I took the following steps:

-   I created this blog!
-   I cleaned and uploaded data from the [Business Master File (BMF)](https://urbaninstitute.github.io/nccs/datasets/bmf/), including only data with an A25 (Arts Education) NTEE (National Taxonomy of Exempt Entities) code.
-   I made a pretty bad visualization in order to test embed-resources
