---
title: "Bar Graph 1: Landscape of Arts Education Nonprofits"
author: "Steven Todd McIntyre II"
date: "2026-02-25"
runtime: shiny
format: 
  dashboard:
    embed-resources: true
    theme: minty
    output:
      orientation: columns
execute:
  warning: false
  message: false
  echo: false
---

```{r}
library(tidyverse)
library(tidytext)
library(here)
library(knitr)
library(shiny)
library(rio)
library(plotly)

```

# Overview

## Column
**How useful can NTEE Codes be in Studying Nonprofits?**

This dashboard will explore United States nonprofit organizations that are coded as "A25" in the National Taxonomy of Exempt Organizations (NTEE), a coding scheme that describes kinds of nonprofit organizations. "A25" is defined by the Urban Institute as "Organizations that provide informal arts educational programming and/or instruction but do not grant diplomas or degrees; or which offer services regarding the arts to educational institutions or to public entities involved in education." Using data from the [Urban Institute's Business Master File (BMF)](https://urbaninstitute.github.io/nccs/datasets/bmf/), I explore the kinds of organizations that use A25 

# Visualization 1: A25 Word Count

## Column

```{r}
a25 <- import(here("data/BMF_A25.csv"))

# set categories of top 50 words
kind_of_org <- c("foundation", "institute", "school", "center", "academy", "association", "guild", "society", "project", "studio", "incorporated", "club", "corporation", "alliance", "productions", "program", "council", "collective", "nfp", "league", "friends")
art_words <- c("arts", "art", "music", "creative", "fine", "design", "theatre", "performing", "workshop", "graphic", "dance", "traditional", "cultural", "hooking", "theater")
education_words <- c("education", "learning", "educational")
locations <- c("american", "community", "international", "county", "valley", "city")
target_audience <- c("artists", "youth", "kids", "artist", "childrens")

a25_top_50 <- a25 |>
  unnest_tokens(output = word, input = ORG_NAME_CURRENT) |>
  select(word) |>
  filter(!word %in% stop_words$word) |>
  count(word) |>
  mutate(word = fct_lump_n(word, n=50, w=n)) |>
  filter(word != "Other") |>
  group_by(word) |>
  summarize(n = sum(n)) |>
  mutate(word=fct_reorder(word, n))

a25_top_50 <- a25_top_50 |>
  mutate(category = case_when(
    word%in%kind_of_org ~ "organization",
    word%in%art_words ~ "art",
    word%in%education_words ~ "education",
    word%in%locations ~ "location",
    word%in%target_audience ~ "people"
  ))

a25_kinds <- a25_top_50 |>
  filter(word%in%kind_of_org)

a25_top_50_plot <- a25_top_50 |>
  ggplot(aes(n, word, fill = category)) +
  geom_col() +
  labs(
    title = "Top 50 Words in A25 \"Arts Education\" Organization Names",
    x = "Instances in A25 Organization Names",
    y = "",
    caption = "Data from the Urban Institute's Business Master File."
  ) +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 5)
  )

ggplotly(a25_top_50_plot)
```


# Summary of Updates

## Column

Removing the relatively poor visualization that was mostly intended to test embed-resources, I've now added a visualization that will be, in some form, in my final project.

In this
